Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
a single sentence
small edits

  \begin{scope}[shift = {(-1,0)}]  
  \node[latent] at (3.5,3) (dx){$\mathcal{D}$};
  \node[latent] at (3.5,1.75) (zp){$p$};
  \node[latent] at (5.5,1.75) (tx){$\theta^{(x)}$};
  \node[obs] at (3.5,0) (xp) {$x$};
  \plate {}{(zp)(xp)(tx)}{$x\in X$};
  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.south) {(b) \\recognition model};
  \draw [->,red] (xp.east) to[out = 0,in = -90] node(nn){} (tx.south);
  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->,red] (dx.south) -- (zp.north);

@@

Our work is an instance of
 \emph{Bayesian Program
  Learning} (BPL; see~\citep{lake2013one,Dechter:2013:BLV:2540128.2540316,ellis2016sampling,DBLP:conf/icml/LiangJK10}).

@@

Searching for programs is extremely difficult because
of the large search space. We ease this difficulty by learning a neural recognition model:

\textbf{Neural recognition model: tractably maxing $\lowerBound$ w.r.t. the
  frontiers.}  Here we train a neural network, $q$, to predict a
distribution over programs conditioned on a task. The objective of $q$
is to assign high probability to programs $p$ where
$\probability[x,p|\mathcal{D},\theta]$ is large.  With $q$ in hand we can find programs for
the frontier $\mathcal{F}_x$ by searching for programs that maximize
$q(p|x)$.
The network $q$ exploits the structure of the DSL $\mathcal{D}$:
rather than directly predicting a distribution over $p$ conditioned on $x$,
it predicts a weight vector, $\theta^{(x)}$, and we define $q(p|x)\triangleq \probability[p|\mathcal{D},\theta = q(x)]$.
%% This approach implements an amortized
%% inference scheme~\cite{le2016inference,ritchie2016deep} for the generative model in
%% Figure~\ref{graphicalModel}.

@@

The recognition model $q$ is a neural network that predicts,
for each task $x\in X$, a weight vector $q(x) = \theta^{(x)}\in \mathbb{R}^{|\mathcal{D}| + 1}$.
Together with the DSL, this defines a distribution over programs,
$\probability[p|\mathcal{D},\theta = q(x)]$.
We abbreviate this distribution as $q(p|x)$.
The crucial aspect of this framing is that the neural network
leverages the structure of the learned DSL,
so it is \emph{not} responsible for
generating programs wholesale.
This taps into the intuition that programming is primarily a top-down activity:
as human programmers, we first decide what kind of
programming constructs we might need to use,
and then we figure out how to assemble them in to the desired program.

>>>>

  \begin{scope}[shift = {(0.7,0)}]  
  \node[latent] at (3.5,3) (dx){$\mathcal{D}$};
  \node[latent] at (3.5,1.75) (zp){$p$};
  \node[latent] at (5.5,1.75) (tx){$\theta^{(x)}$};
  \node[obs] at (3.5,0) (xp) {$x$};
  \plate {}{(zp)(xp)(tx)}{$x\in X$};
  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.south) {(b) \\recognition model};
  \draw [->,red] (xp.east) to[out = 0,in = -90] node(nn){} (tx.south);
  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->,red] (dx.south) -- (zp.north);

@@

Our work is an instance of
 Bayesian Program
 Learning (BPL; see~\citep{lake2013one,Dechter:2013:BLV:2540128.2540316,ellis2016sampling,DBLP:conf/icml/LiangJK10}). Previous BPL systems have largely assumed a fixed DSL (but see~\cite{DBLP:conf/icml/LiangJK10}),
 and our contribution here is a general scheme for getting BPL off the ground with less hand-engineering of the DSL.

@@

Searching for programs is hard because
of the large combinatorial search space. We ease this difficulty by learning a neural recognition model:

\textbf{Neural recognition model: tractably maxing $\lowerBound$ w.r.t. the
  frontiers.}  Here we train a neural network, $q$, to predict a
distribution over programs conditioned on a task. The objective of $q$
is to assign high probability to programs $p$ where
$\probability[x,p|\mathcal{D},\theta]$ is large.  With $q$ in hand we can find programs for
the frontier $\mathcal{F}_x$ by searching for programs that maximize
$q(p|x)$.
The network $q$ exploits the structure of the DSL $\mathcal{D}$:
rather than directly predicting a distribution over $p$ conditioned on $x$,
it predicts a weight vector, $\theta^{(x)}$, and we define $q(p|x)\triangleq \probability[p|\mathcal{D},\theta = q(x)]$.
This taps into the intuition that programming is primarily a top-down activity:
as human programmers, we first decide what kind of
programming constructs we might need to use,
and then we figure out how to assemble them in to the desired program.
%% This approach implements an amortized
%% inference scheme~\cite{le2016inference,ritchie2016deep} for the generative model in
%% Figure~\ref{graphicalModel}.

@@

The recognition model $q$ is a neural network that predicts,
for each task $x\in X$, a weight vector $q(x) = \theta^{(x)}\in \mathbb{R}^{|\mathcal{D}| + 1}$.
Together with the DSL, this defines a distribution over programs,
$\probability[p|\mathcal{D},\theta = q(x)]$.
We abbreviate this distribution as $q(p|x)$.
The crucial aspect of this framing is that the neural network
leverages the structure of the learned DSL,
so it is \emph{not} responsible for
generating programs wholesale.
